\documentclass[12pt]{article}
\newcommand\tab[1][1cm]{\hspace{#1}}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{color}
\usepackage{textcomp}
\usepackage{sectsty}
\usepackage{graphicx}
\pagenumbering{gobble}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
\lstdefinestyle{mystyle}{
	backgroundcolor=\color{backcolour},   
	commentstyle=\color{codegreen},
	keywordstyle=\color{magenta},
	numberstyle=\tiny\color{codegray},
	stringstyle=\color{codepurple},
	basicstyle=\footnotesize,
	breakatwhitespace=false,         
	breaklines=true,                 
	captionpos=b,                    
	keepspaces=true,                 
	numbers=left,                    
	numbersep=5pt,                  
	showspaces=false,                
	showstringspaces=false,
	showtabs=false,                  
	tabsize=2
}

\lstset{style=mystyle}


\begin{document}
\author{Eric Pereira\\
	CSE3120: Section 01}
\date{September 15\textsuperscript{th}, 2018}
\title{Homework 4}
\maketitle

\section*{4.1.10}

\subsection*{2. \normalsize (True/False): The destination operand of a MOV instruction cannot be a segment register}
\paragraph{Answer: }False

\section*{4.9.1}

\subsection*{5. \normalsize What will be the value of the Parity flag after the following lines execute?\\
\texttt{mov al,1} \\
\texttt{add al,3}}
\paragraph{Answer: }0

\subsection*{6. \normalsize What will be the value of EAX and the Sign flag after the following lines execute? \\
\texttt{mov eax,5} \\
\texttt{sub eax,6}}
\paragraph{Answer: }1

\subsection*{12. \normalsize (Yes/No): Is it possible to set the Overflow flag if you add a positive integer to a negative integer?}
\paragraph{Answer: } No

\subsection*{14. \normalsize (Yes/No): Is it possible for the NEG instruction to set the Overflow flag?}
\paragraph{Answer: }Yes

\section*{4.9.2}

\subsection*{1. \normalsize Write a sequence of MOV instructions that will exchange the upper and lower words in a doubleword variable named three.}
\paragraph{Answer: } 
	mov eax, word ptr three \\
	mov ebx, word ptr three+2 \\
	mov three, ebx \\
	mov word ptr three+2, eax \\

\subsection*{10. \normalsize Write a sequence of two instructions that set both the Carry and Overflow flags at the same time}
\paragraph{Answer: } 
	mov al,70h \\
	add al,90h \\

\section*{4.10}

\subsection*{1. Converting from Big Endian to Little Endian \\ 
	\normalsize Write a program that uses the variables below and MOV instructions to copy the value from bigEndian to littleEndian, reversing the order of the bytes. The number’s 32-bit value is understood
	to be 12345678 hexadecimal. \\
\texttt{.data \\
	bigEndian BYTE 12h,34h,56h,78h \\
	littleEndian DWORD?}}
\paragraph{Answer: } 
	.code \\ 
	main PROC \\
	mov al,[bigEndian+3] \\
	mov BYTE PTR [littleEndian],al \\
	mov al,[bigEndian+2] \\
	mov BYTE PTR [littleEndian+1],al \\
	mov al,[bigEndian+1] \\
	mov BYTE PTR [littleEndian+2],al \\
	mov al,[bigEndian] \\
	mov BYTE PTR [littleEndian+3],al \\

\end{document}