\documentclass[aspectratio=169]{beamer}

\input{../../presentationPream}

\usetheme{PaloAlto}
\usecolortheme{whale}

\title[]{Revamp of High Energy Physics Laboratory's Computer Systems}
\author[]{Josef Bostik \\Eric Pereira \\Ryan Wojtyla}
\date{April 19, 2019}

\begin{document}

%----------BEGIN TITLE----------

\begin{frame}
  \titlepage
\end{frame}

%-----------END TITLE-----------

%----------BEGIN GOALS----------

\section{Milestone 6 Goals}

\begin{frame}
  
  \frametitle{Milestone 6 Progress}

\begin{adjustwidth}{-0.4cm}{}
	
	 \begin{center}
		\begin{tabular}{|c|c|c|c|}
			\hline
			Task & Progress & Notes\\
			\hline
			Polish Cluster Documentation & 100\% & \\
			Polish MTS Documentation & 100\% &  \\
			Create MTS Automation Script & 70\% &  \\
			Integrate Remainder of Cluster Components & 50\% & \begin{tabular}{@{}c@{}} NAS-0 must be included \end{tabular} \\
			Assist Researchers & 100\% & \begin{tabular}{@{}c@{}} helping out with
				general\\ problems as they arise \end{tabular} \\
			Create GEM computer Backups & 50\% & \begin{tabular}{@{}c@{}} issues with
				hardware \\ requirements \end{tabular} \\
			
			\hline
		\end{tabular}
	\end{center}
 
\end{adjustwidth}
  
\end{frame}

%-----------END GOALS-----------

%----------BEGIN GEM COMPUTERS----------

\section{GEM Computers}

\begin{frame}

  \frametitle{GEM Computers}

  \begin{itemize}
    \item RAID array optimized for storage, preventing redundancy.
    \item Package and software installation problems.
  \end{itemize}

\end{frame}

%-----------END GEM COMPUTERS-----------

%----------BEGIN CLUSTER----------

\section{Compute Cluster}

\begin{frame}

  \frametitle{Compute Cluster}

  \begin{itemize}
  \item NAS-0 hard drive issues have been slowing its integration into the cluster.
    \begin{itemize}
      \item Confusing drive labels makes replacing several drives challenging.
    \end{itemize}
  \item SE software installation and configuration is being used for training.
    \begin{itemize}
    \item The sysadmins need to get used to working without me.
    \item They will gain valuable, first-hand knowledge about how the
      cluster is put together.
    \end{itemize}
  \end{itemize}
  
\end{frame}

%-----------END CLUSTER-----------

\section{Muon Tomography Station}

%----------BEGIN EXISTING MTS----------

\subsection{Existing MTS}

\begin{frame}

  \frametitle{Existing MTS}

  \begin{itemize}
  \item The MTS is being operated in a degraded state.
    \begin{itemize}
    \item Not all sides of the detector are operational.
    \item Data can still be collected.
    \end{itemize}
  \item User-friendliness script is being written.
    \begin{itemize}
    \item Packaging provided operation instructions into an easy-to-use
      script.
    \item Ease workload of MTS researchers.
    \end{itemize}
  \end{itemize}

\end{frame}

%-----------END EXISTING MTS-----------

%----------BEGIN DEVELOPMENT MTS----------

\subsection{Development MTS}

\begin{frame}

  \frametitle{Development MTS}

  \begin{itemize}
    \item Attempted to build AMORE from source
    \item Makefile 'Makefile.arch' was not found during build configuration, but
      we did find the file in another directory, and made AMORE reliant on that
      Makefile instead.
    \item Build got further, but a few header files weren't found. The
      configuration seems to not know the proper location to find some files.
    \item Continued attempting to get the previous build of AMORE working,
    	  manually changing dependencies to our new version of root.
  \end{itemize}

\end{frame}

%-----------END DEVELOPMENT MTS-----------

%----------BEGIN DOCUMENTATION----------

\section{Documentation}

\begin{frame}

  \frametitle{Documentation}

  \begin{itemize}
    \item Manuals have been created for:
      \begin{itemize}
        \item the rebuild of the computing cluster.
        \item the construction of the development MTS machine.
      \end{itemize}
    \item These manuals are incomplete, but they are living documents to be
      lengthened as the two projects develop.
  \end{itemize}


\end{frame}

%-----------END DOCUMENTATION-----------

%----------BEGIN MILESTONE 5 GOALS----------

\section{Future Work}

\begin{frame}

  \frametitle{Future Work}

  \begin{itemize}
    \item Computing Cluster
      \begin{itemize}
        \item Fully integrate remaining cluster component.
        \item 
      \end{itemize}
  \end{itemize}

\end{frame}

%-----------END MILESTONE 6 GOALS-----------

%----------BEGIN QUESTIONS----------

\section{Questions}

\begin{frame}

  \frametitle{Questions}

  \begin{center}
    {\fontsize{200}{200}\selectfont ?}
  \end{center}
  
\end{frame}

%-----------END QUESTIONS-----------


\end{document}
